A free/open-source machine translation system for English to Kazakh

### 2015-03-05 engkaz-eamt-2015/engkaz-eamt-2015.tex
changed <..>
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@59226 72bbbca6-d526-0410-a7d9-f06f51895060

MT systems have some mistakes in translations, which was shown in <...> brackets.\todo{you used *!} Google MT system 
has a higher BLEU score, but in translation separate phrases, it has common error: it does not assign 
the right possessive and case. Sanasoft system has more errors with choosing not right translations 
and out of vocabulary words.

>>>>

MT systems have some mistakes in translations, which was shown with *.\todo{DONE you used *!} Google MT system 
has a higher BLEU score, but in translation separate phrases, it has common error: it does not assign 
the right possessive and case. Sanasoft system has more errors with choosing not right translations 
and out of vocabulary words.
